Test data

### 2022-07-21 Shiny/Test/Test data.Rmd
Donation growth KPI.

### Private donation growth
```{r}
kreft_excel |> 
  select(year, revenue_private_contributions) |> 
  pivot_wider(names_from = year, values_from = revenue_private_contributions) |> 
  mutate(
    growth = `2020` / `2019` * 100
  )

?pivot_wider
```

>>>>

### Private donation growth
```{r}
kreft_excel |> 
  transmute(
    growth = revenue_private_contributions[1] / revenue_private_contributions[2] * 100
  ) |> 
  pull() |> 
  first()

?pull
```
